---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

For data analysis (or even pre-processing), R can be a useful tool. In R, we can use practices to generate readable, reusable and testable code. By maintaining clean scripts that have comments regarding every block of code (i.e what is it doing), having a README for the project folder that states what modules and dependencies are needed, and frequently committing changes using a version control software (like git) - all these help maintain clean reproducible data analysis practices. Another thing that I like doing is keeping scripts short by generating more function files and calling on those from main scripts.

3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 
```{r}
(4^13)^(1/2)

```


4) Push this homework to the GitHub repository for the homework. 





